---
title: "Supplementary materials for the imitation meta-analysis REVISED"
author: "JD"
date: "31 August 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Results of the main manuscript

## Results for the meta-analysis of neonatal imitation

```{r preamble, echo=FALSE, include=FALSE, warning=FALSE}

rm(list=ls())
setwd("C:\\Users\\Topsy\\Documents\\imitation")
library(metafor)
library(rmeta)
library(data.table)
library(plyr)

dat <- read.csv("imitation meta revised.csv")

## Identify variables ##

dat$ID.L1 <- as.factor(dat$PaperID) # The ID for the overall paper
dat$ID.L2 <- as.factor(dat$Study) # The ID for the independent sample (may be >1 per paper)
dat$First.author <- as.factor(dat$Author) # First author
dat$Year <- as.numeric(dat$Year) # Year of publication
dat$Age <- as.numeric(dat$Age..days.)  # Average age of neonates, in days
dat$Pres.time <- as.numeric(dat$Presentation.time) # Presentation time, in seconds
dat$Resp.time <- as.numeric(dat$Response.time) # Response time, in seconds
dat$Gesture <- as.factor(dat$Gesture) # Target gesture

## Effect sizes ##
dat$yi.1 <- as.numeric(dat$d) # Effect size, may be >1 per independent sample
dat$vi.1 <- as.numeric(dat$var.d.) # Variance of the effect size in coding sheet
## using variance of d calculated from N instead of from the effect size calculation, which gives an answer closer to the original study for studies with lots of estimates
dat$v <- (((dat$N+dat$N)/(dat$N*dat$N))+(dat$yi.1^2/(2*(dat$N+dat$N-2))))*((dat$N+dat$N)/(dat$N+dat$N-2))
# With Hedges' correction for small samples
dat$J <- (1-(3/((4*(dat$N))-9)))
dat$gi.1 <- dat$yi.1*dat$J

tgt <- dat # choose dataset

```

## Systematic search results

The final set of `r nlevels(tgt$ID.L1)` papers eligible for the meta-analysis contained  `r nlevels(tgt$ID.L2)` independent samples and `r length(tgt$yi.1)` effect sizes for all gestures.

## Primary meta-analysis, all gestures

```{r primary meta-analysis, echo=FALSE, include=FALSE, warning=FALSE}
tgt <- dat # choose dataset
### multilevel random-effects model
rml <- rma.mv(gi.1, v, random = list(~ 1 | ID.L1, ~ 1 | ID.L2), data=tgt)
Isq <- 100*(rml$QE-(nrow(tgt)-1))/rml$QE
```

The multilevel meta-analysis of neonatal imitation across all gestures included a total of `r rml$k` effect sizes from `r nlevels(tgt$ID.L2)` independent groups, reported in `r nlevels(tgt$ID.L1)` studies. When all studies were combined, infants produced the target gesture more to the model than to the comparison, and this effect was statistically significant (d = `r round(rml$b, 2)`, 95% CI = `r round(rml$ci.lb, 2)` to `r round(rml$ci.ub, 2)`, p < .001). 

The multilevel meta-analysis revealed substantial heterogeneity in the set of neonatal imitation studies, both at the study level (sigma^2,1 = `r round(rml$sigma2[1],2)`) and at the subgroup level (sigma^2,2 = `r round(rml$sigma2[2],2)`), Q(`r nrow(tgt)-1`) = `r round(rml$QE,2)`, p = `r round(rml$QE,3)`. Based on the Q statistic, the percentage of variance in the dataset due to heterogeneity between estimates is approximately `r round(Isq,2)`%  (I-squared).

### Forest plot

```{r setup forest plot, echo=FALSE, include=FALSE, warning=FALSE}

tgt <- dat # choose dataset

# First get single estimate per independent sample 

levels(tgt$ID.L2) # number of independent samples
IDs <- unique(tgt$ID.L2) # list of unique IDs (identifiers for each sample)
k <- length(IDs) # number of independent samples
y <- c("Paper","k","estimate","se","p","N") # create an empty list with headings
# for loop fills the list with required information for each sample
for(i in 1:k){
  temp <- tgt[tgt$ID.L2==IDs[i],]
  a <- rma(gi.1, v, data=temp)
  b <- c(as.character(temp$ID.L2[1]),a$k,a$b,a$se,a$pval,as.character(temp$N[1]))
  y <- rbind(y, b)
}  

# tidy the dataset
colnames(y) <- as.character(unlist(y[1,])) 
y = y[-1, ]

# optional: write csv with new estimates
# write.csv(y, "Imitation meta-analysis combined estimates.csv")

# get into plotting dataframe
z <- as.data.frame(y)
z$Name <- revalue(z$Paper, 
                  c("Anisfeld2001_1"="Anisfeld et al. 2001", 
                    "Coulon2013_1"="Coulon et al. 2013 Condition 1",
                    "Coulon2013_2"="Coulon et al. 2013 Condition 2",
                    "Field1982_1"="Field et al. 1982",
                    "Field1983_1"="Field et al. 1983",
                    "Fontaine1984_1"="Fontaine 1984",
                    "Heimann1985_1"="Heimann & Schaller 1985",
                    "Heimann1989_1"="Heimann et al. 1989 Time 1",
                    "Heimann1989_2"="Heimann et al. 1989 Time 2",   
                    "Heimann1998_1"="Heimann 1998",
                    "Kennedy2017_1"="Kennedy-Costantini 2017",
                    "Koepke1983_1"="Koepke et al. 1983",  
                    "Legerstee1991_1"="Legerstee 1991",
                    "Sho0000_1"="Sho et al. unpublished",
                    "McKenzie1983_1"="McKenzie & Over 1983",
                    "Meltzoff1977_1"="Meltzoff & Moore 1977 Experiment 1",
                    "Meltzoff1977_2"="Meltzoff & Moore 1977 Experiment 2",
                    "Meltzoff1983_1"="Meltzoff & Moore 1983",
                    "Meltzoff1989_1"="Meltzoff & Moore 1989",
                    "Meltzoff1992_1"="Meltzoff & Moore 1992",
                    "Meltzoff1994_1"="Meltzoff & Moore 1994",
                    "Nagy2007_1"="Nagy et al. 2007",
                    "Nagy2014_1"="Nagy et al. 2014 Left condition",
                    "Nagy2014_2"="Nagy et al. 2014 Right condition",
                    "Nagy2014_3"="Nagy et al. 2014 Both condition",
                    "Oostenbroek2016_1"="Oostenbroek et al. 2016 1 week   old",
                    "Oostenbroek2016_2"="Oostenbroek et al. 2016 3 weeks old",
                    "Oostenbroek2016_3"="Oostenbroek et al. 2016 6 weeks old",
                    "Reissland1988_1"= "Reissland 1988",
                    "Soussignan2011_1"="Soussignan et al. 2011",
                    "Ullstadius1998_1"="Ullstadius 1998"))

z$Year <- readr::parse_number(z$Paper) # get the publication years so that samples can be ordered chronologically
z$Year[z$Year==0000]<-2014 # unpublished study has 0000 in the study ID but data were collected in 2014
z$estimate <- as.numeric((as.character(z$estimate)))
z$N <- as.numeric((as.character(z$N)))
## using variance of d derived from N instead of from the meta-analysis, which gives an answer closer to the original study for studies with lots of estimates
z$v <- (((z$N+z$N)/(z$N*z$N))+(z$estimate^2/(2*(z$N+z$N-2))))*((z$N+z$N)/(z$N+z$N-2))
z$J <- (1-(3/((4*(z$N))-9)))
z$g <- z$estimate*z$J
z$seN <- sqrt(z$v)
z$lower <- z$g - (1.96*z$seN)
z$upper <- z$g + (1.96*z$seN)
```

```{r forest plot, fig.height=4, fig.width=8, dev='svg', echo=FALSE, warning=FALSE, message=FALSE}

z_dt <- setDT(z)
setkey(z_dt,Year,Name)
z <- z_dt
z$ord <- as.numeric(row.names(z))

# plot with ggplot
require(ggplot2)

fp <- ggplot(data=z, (
             aes(x=reorder(Name,-ord),
                 y=g,
                 ymin=lower,
                 ymax=upper))) +
  geom_pointrange() + 
  geom_hline(yintercept=rml$b, lty=2) +  # add a dotted line at x=1 after flip
  geom_hline(yintercept=0, lty=2, col="red") +  # add a dotted line at x=1 after flip
  coord_flip() +  # flip coordinates (puts labels on y axis)
  xlab("Study") + ylab("Effect size (95% CI)") +
  theme_bw() +
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.border=element_blank(),
        axis.line=element_line(),
        legend.position='none') # APA format
print(fp)

```

## Tongue protrusion only

```{r tongue protrusion only, echo=FALSE, include=FALSE, warning=FALSE}
tgt <- dat # choose dataset
subTP <- rma.mv(gi.1, v, 
                 subset = (Gesture=="Tongue protrusion"), 
                 random = list(~ 1 | ID.L1, ~ 1 | ID.L2), data=tgt)
subTP
```

The multilevel meta-analysis of neonatal imitation of tongue protrusion included a total of `r subTP$k` effect sizes. Neonates produced more tongue protrusions in response to a tongue protrusion model than in response to other models (d = `r round(subTP$b, 2)`, 95% CI = `r round(subTP$ci.lb, 2)` to `r round(subTP$ci.ub, 2)`, p = `r round(subTP$pval, 3)`).

## Moderator Analyses

### Results for Table 2

```{r presentation mod, echo=FALSE, include=FALSE, warning=FALSE}
tgt <- dat # choose dataset

Pres <- rma.mv(gi.1,v,
                 mods=Presentation.time..seconds., 
                 random = list(~ 1 | ID.L1, ~ 1 | ID.L2), 
                 data=tgt)
summary(Pres)

Resp <- rma.mv(gi.1,v,
                 mods=Response.time..seconds., 
                 random = list(~ 1 | ID.L1, ~ 1 | ID.L2), 
                 data=tgt)
summary(Resp)

Simul <- rma.mv(gi.1,v,
                 mods=Modelling.while.responding, 
                 random = list(~ 1 | ID.L1, ~ 1 | ID.L2), 
                 data=tgt)
summary(Simul)

Baseline <- rma.mv(gi.1,v,
                 mods=Baseline, 
                 random = list(~ 1 | ID.L1, ~ 1 | ID.L2), 
                 data=tgt)
summary(Baseline)


coef<-NULL
coef$moderator <- c("Presentation time","Response time","Modelling while responding","Baseline or active control")
coef$b <- c(Pres$b[2],Resp$b[2],Simul$b[2],Baseline$b[2])
coef$se <- c(Pres$se[2],Resp$se[2],Simul$se[2],Baseline$se[2])
coef$p <- c(Pres$pval[2],Resp$pval[2],Simul$pval[2],Baseline$pval[2])

```

**Table 2.** Summary of the impact of methodological variations. Analyses were meta-regressions of each variable on the effect size.

```{r kable, echo=FALSE, warning=FALSE}
library(knitr)
#names(coef) <- c("Moderator","","","")
coef<-as.data.frame(coef)
kable(coef, digits=3)
```

## Publication bias

```{r publication bias, echo=FALSE, include=FALSE, warning=FALSE}

tgt <- dat # choose dataset
# classical Egger test equation is a weighted linear OLS regression with standard error as a covariate
## y = a + B*se, weighted by 1/se^2 with e ~ N(0,se^2*phi)
# where phi is an unknown multiplicative dispersion parameter
# This is adjusted in Moreno et al (2009) because multiplicative error term not consistent with additive error in typically used variance-weighted meta-regression
# y = a + B*se weighted by 1/se^2 with e ~ N(0,se^2)  fixed effects
# incorporating random effects: additive component of between-study variance tau^2
# y = a + B*se + mu, weighted by 1/(se^2+tau^2) where mu~N(0,tau^2) and e~N(0,se^2)
# mu and e are estimated from the data

# adapted Egger test from Moreno et al 2009
# adding levels extending the random effect model by adding the extra variance term to the weight (method 1)
tausq1 <- rml$sigma2[1]
tausq2 <- rml$sigma2[2]
egger1 <- lm(tgt$yi.1 ~ tgt$v, weights=1/(tgt$v+tausq1+tausq2))
segger1 <- summary(egger1)

# adding a random effects term to meta-analysis model with variance as a predictor (method 2)
egger2 = rma.mv(gi.1,v, mod = v, random = ~1|PaperID, data = tgt)
segger2 <- summary(egger2)

```

**Egger test.** The tests revealed significant asymmetry, which is consistent with that expected from publication bias, t = `r round(segger1$coefficients[6],3)`, p = `r round(segger1$coefficients[8], 4)`. 

### Funnel plot

**Funnel plot 1: All estimates.** Funnel plot with all gestures from all subgroups. Points are not independent. Does not account for clustering. Effect sizes from Meltzoff & Moore (1977) are circled.

``` {r funnel plot 1, echo=FALSE, warning=FALSE}

tgt <- dat # choose dataset

# plot with ggplot
# modified from sakaluk.wordpress.com

# identify variables for the plot
estimate = rml$b
se = rml$se
tgt$se <- sqrt(tgt$v) # to match forest, this should be based on N
tgt$inv <- as.numeric(1/tgt$se)

# create lines for the funnel
se.seq=seq(0, max(tgt$se), 0.001)
ll95 = estimate-(1.96*se.seq)
ul95 = estimate+(1.96*se.seq)
ll99 = estimate-(3.29*se.seq)
ul99 = estimate+(3.29*se.seq)
meanll95 = estimate-(1.96*se)
meanul95 = estimate+(1.96*se)

# create data frame for plot lines
dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)

# identify the first published study with red coloured points
tgt$Meltzoff <- "0" 
tgt$Meltzoff[tgt$ID.L1=="Meltzoff1977"]="1"
tgt$Meltzoff <- as.numeric(tgt$Meltzoff)

# create data frame for plot points
yi <- tgt$yi.1
sd <- tgt$se
M <- tgt$Meltzoff
newdat <- cbind.data.frame(yi,sd,M)
newdat$M <- as.factor(newdat$M)
sub <- newdat[newdat$M==1,]

# make the plot
fp = ggplot(aes(x = sd, y = yi), data = newdat) +
  geom_point(aes(fill=M,shape=M), data=newdat) +
  geom_point(aes(x = sd, y = yi), data = sub) +
  geom_point(shape=1, size=6, data = sub) +
  xlab('Standard Error') + ylab('Effect size')+
  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
  geom_segment(aes(x = min(se.seq), y = estimate, xend = max(se.seq), yend = estimate), data=dfCI) +
  scale_x_reverse()+
  coord_flip()+
  theme_bw() +
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.border=element_blank(),
        axis.line=element_line(),
        legend.position='none') # APA format

fp

````


# Results for the supplementary material

## Moderator analysis: Infant age
```{r supplementary (infant age), echo=FALSE, include=FALSE, warning=FALSE}
tgt <- dat # choose dataset
Age <- rma.mv(gi.1,v,
              mods=Age, 
              random = list(~ 1 | ID.L1, ~ 1 | ID.L2), 
              data=tgt)
```
The moderator analysis included a total of `r Age$k` effect sizes. The moderator effect of age on study effect size was small and not significant (b = `r round(Age$b[2], 2)`, se = `r round(Age$se[2], 2)`, 95% CI = `r round(Age$ci.lb[2], 2)` to `r round(Age$ci.ub[2], 2)`, p = `r round(Age$pval[2], 3)`). 

## Sensitivity analysis: Restricting the meta-analysis to infants under 4 weeks old
```{r supplementary (under 4 weeks), echo=FALSE, include=FALSE, warning=FALSE}
tgt <- dat[dat$Age <= 28,] # choose dataset
# meta-analysis
wks <- rma.mv(gi.1,v,
              random = list(~ 1 | ID.L1, ~ 1 | ID.L2), 
              data=tgt)
# publication bias
tausq1 <- wks$sigma2[1]
tausq2 <- wks$sigma2[2]
egger1 <- lm(tgt$yi.1 ~ tgt$v, weights=1/(tgt$v+tausq1+tausq2))
segger1 <- summary(egger1)
egger2 = rma.mv(gi.1,v, mod = v, random = ~1|PaperID, data = tgt)
segger2 <- summary(egger2)
```
The sensitivity analysis included a total of `r wks$k` effect sizes. The overall effect of imitation in infants under 4 weeks was large and significant (b = `r round(wks$b, 2)`, se = `r round(wks$se, 2)`, 95% CI = `r round(wks$ci.lb, 2)` to `r round(wks$ci.ub, 2)`, p = `r round(wks$pval, 3)`). The publication bias result was similar to the overall meta-analysis (t = `r round(segger1$coefficients[6],3)`, p = `r round(segger1$coefficients[8], 4)`).

## Sensitivity analysis: Meta-analysis with a single estimate per independent sample
```{r supplementary (one estimate per sample), echo=FALSE, include=FALSE, warning=FALSE}
tgt <- z # choose dataset
# meta-analysis
rmz <- rma(estimate,sei=seN,
            data=z)
# publication bias
tgt$vi <- tgt$v
egger1 <- lm(tgt$estimate ~ tgt$vi, weights=1/(tgt$vi))
segger1 <- summary(egger1)
egger2 = regtest(rmz, model="lm", predictor="sei")
segger2 <- summary(egger2)
# trim and fill - note, this has not been implemented with multilevel models and so is only appropriate for results with a single estimate per study
tf1 <- trimfill(rmz, estimator="L0",side=NULL)
```
The sensitivity analysis included a total of `r rmz$k` effect sizes. The overall effect of imitation with a single effect estimate per independent sample was large and significant (d = `r round(rmz$b, 2)`, se = `r round(rmz$se, 2)`, 95% CI = `r round(rmz$ci.lb, 2)` to `r round(rmz$ci.ub, 2)`, p = `r round(rmz$pval, 3)`). The publication bias result was similar to the overall meta-analysis (t = `r round(segger1$coefficients[6],3)`, p = `r round(segger1$coefficients[8], 4)`).



## Tongue protrusion only
```{r supplementary (tongue protrusion), echo=FALSE, include=FALSE, warning=FALSE}
TP <- dat[dat$Gesture=="Tongue protrusion",]
tgt <- TP # choose dataset
# meta-analysis
rmTP <- rma.mv(gi.1,v,
              random = list(~ 1 | ID.L1, ~ 1 | ID.L2), 
              data=TP)
# publication bias
tausq1 <- rmTP$sigma2[1]
tausq2 <- rmTP$sigma2[2]
egger1 <- lm(tgt$yi.1 ~ tgt$v, weights=1/(tgt$v+tausq1+tausq2))
segger1 <- summary(egger1)
egger2 = rma.mv(gi.1,v, mod = v, random = ~1|PaperID, data = tgt)
segger2 <- summary(egger2)
```
The sensitivity analysis included a total of `r rmTP$k` effect sizes. The overall effect of imitation measured using only tongue protrusion was large and significant (d = `r round(rmTP$b, 2)`, se = `r round(rmTP$se, 2)`, 95% CI = `r round(rmTP$ci.lb, 2)` to `r round(rmTP$ci.ub, 2)`, p = `r round(rmTP$pval, 3)`). The publication bias result was similar to the overall meta-analysis (t = `r round(segger1$coefficients[6],3)`, p = `r round(segger1$coefficients[8], 4)`).

### Tongue protrusion with baseline comparison only
```{r supplementary (tongue protrusion compared to baseline), echo=FALSE, include=FALSE, warning=FALSE}
tgt <- TP[TP$Baseline==1,] # choose dataset
# meta-analysis
rmTPB <- rma.mv(gi.1,v,
              random = list(~ 1 | ID.L1, ~ 1 | ID.L2), 
              data=tgt)
# publication bias
tausq1 <- rmTPB$sigma2[1]
tausq2 <- rmTPB$sigma2[2]
egger1 <- lm(tgt$yi.1 ~ tgt$v, weights=1/(tgt$v+tausq1+tausq2))
segger1 <- summary(egger1)
egger2 = rma.mv(gi.1,v, mod = v, random = ~1|PaperID, data = tgt)
segger2 <- summary(egger2)
```
The sensitivity analysis included a total of `r rmTPB$k` effect sizes. The overall effect of imitation measured using only tongue protrusion compared to baseline was large and significant (d = `r round(rmTPB$b, 2)`, se = `r round(rmTPB$se, 2)`, 95% CI = `r round(rmTPB$ci.lb, 2)` to `r round(rmTPB$ci.ub, 2)`, p = `r round(rmTPB$pval, 3)`). The publication bias result was not significant, in contrast to the overall meta-analysis (t = `r round(segger1$coefficients[6],3)`, p = `r round(segger1$coefficients[8], 4)`).

### Tongue protrusion with active comparison (mouth opening) only
```{r supplementary (tongue protrusion compared to active control), echo=FALSE, include=FALSE, warning=FALSE}
tgt <- TP[TP$Baseline==0,] # choose dataset
# meta-analysis
rmTPA <- rma.mv(gi.1,v,
              random = list(~ 1 | ID.L1, ~ 1 | ID.L2), 
              data=tgt)
# publication bias
tausq1 <- rmTPA$sigma2[1]
tausq2 <- rmTPA$sigma2[2]
egger1 <- lm(tgt$yi.1 ~ tgt$v, weights=1/(tgt$v+tausq1+tausq2))
segger1 <- summary(egger1)
egger2 = rma.mv(gi.1,v, mod = v, random = ~1|PaperID, data = tgt)
segger2 <- summary(egger2)
```
The sensitivity analysis included a total of `r rmTPA$k` effect sizes. The overall effect of imitation measured using only tongue protrusion compared to mouth opening was large and significant (d = `r round(rmTPA$b, 2)`, se = `r round(rmTPA$se, 2)`, 95% CI = `r round(rmTPA$ci.lb, 2)` to `r round(rmTPA$ci.ub, 2)`, p = `r round(rmTPA$pval, 3)`). The publication bias result was similar to the overall meta-analysis (t = `r round(segger1$coefficients[6],3)`, p = `r round(segger1$coefficients[8], 4)`).

## Moderator analysis: Facial and non-facial gestures
```{r supplementary (facial and non-facial gestures), echo=FALSE, include=FALSE, warning=FALSE}

tgt <- dat # choose dataset
# recode all gestures to a new variable facial or non-facial gestures
tgt$face <- revalue(tgt$Gesture, 
                 c("Arm raising"="0", 
                   "Cheek swelling"="0",
                   "CLICK sound"="1",
                   "EEE sound"="1",
                   "Eye closing"="1",
                   "Finger movement"="0",
                   "Finger movement partial"="0",
                   "Finger protrusion"="0",
                   "Grasping"="0",
                   "Hand movement"="0",
                   "Hand opening"="0",
                   "Hand to mouth"="0",
                   "Happy expression (wide lips)"="1",
                   "Happy face"="1",
                   "Head movement"="0",
                   "Index finger point"="0",
                   "Lip protrusion"="1",
                   "Lip spreading"="1",
                   "MMM sound"="1",
                   "Mouth opening"="1",
                   "Partial mouth opening"="1",
                   "Partial tongue protrusion"="1",
                   "Pursed lips"="1",
                   "Sad expression (pouting lips)"="1",
                   "Sad expression (furrowed brow)"="1",
                   "Sad face"="1",
                   "Sequential finger movement"="0",
                   "Surprised expression (wide open mouth)"="1",
                   "Surprised expression (widened eyes)"="1",
                   "Tongue protrusion"="1",
                   "Widened lips"="1"))
tgt$face[tgt$face=="0"] <- 0
tgt$face[tgt$face=="1"] <- 1
tgt$face2 <- as.numeric(tgt$face)

# meta-analysis
faces <- rma.mv(gi.1, v, random = list(~ 1 | ID.L1, ~ 1 | ID.L2), 
                mods=face2,
                data=tgt)
# publication bias
tausq1 <- faces$sigma2[1]
tausq2 <- faces$sigma2[2] 
egger1 <- lm(tgt$yi.1 ~ tgt$v, weights=1/(tgt$v+tausq1+tausq2))
segger1 <- summary(egger1)
egger2 = rma.mv(gi.1,v, mod = v, random = ~1|PaperID, data = tgt)
segger2 <- summary(egger2)
```
The sensitivity analysis included a total of `r faces$k` effect sizes. The overall effect of imitation measured using only tongue protrusion compared to mouth opening was large and significant (b = `r round(faces$b[2], 2)`, se = `r round(faces$se[2], 2)`, 95% CI = `r round(faces$ci.lb[2], 2)` to `r round(faces$ci.ub[2], 2)`, p = `r round(faces$pval[2], 3)`). 
## Moderator analysis: Imputed data
```{r supplementary (imputed data), echo=FALSE, include=FALSE, warning=FALSE}

tgt <- dat # choose dataset
# recode all gestures to a new variable facial or non-facial gestures
tgt$imput <- revalue(tgt$ID.L1, 
                    c("Anisfeld2001"="0",
                      "Coulon2013"="0",
                      "Field1982"="0",
                      "Field1983"="0",
                      "Fontaine1984"="0",
                      "Heimann1985"="0",
                      "Heimann1989"="0",
                      "Heimann1998"="0",
                      "Kennedy2017"="0",
                      "Koepke1983"="1",
                      "Legerstee1991"="1",
                      "Sho0000"="0",
                      "McKenzie1983"="1",
                      "Meltzoff1977"="1",
                      "Meltzoff1983"="1",
                      "Meltzoff1989"="0",
                      "Meltzoff1992"="0",
                      "Meltzoff1994"="0",
                      "Nagy2007"="0",
                      "Nagy2014"="0",
                      "Oostenbroek2016"="0",
                      "Reissland1988"="0",
                      "Soussignan2011"="1",
                      "Ullstadius1998"="1"))

tgt$imput <- as.numeric(tgt$imput)
# meta-analysis
imput <- rma.mv(gi.1, v, random = list(~ 1 | ID.L1, ~ 1 | ID.L2),
                mods=imput, 
                data=tgt)
# publication bias
tausq1 <- imput$sigma2[1]
tausq2 <- imput$sigma2[2]
egger1 <- lm(tgt$yi.1 ~ tgt$v, weights=1/(tgt$v+tausq1+tausq2))
segger1 <- summary(egger1)
egger2 = rma.mv(gi.1,v, mod = v, random = ~1|PaperID, data = tgt)
segger2 <- summary(egger2)
```
The sensitivity analysis included a total of `r imput$k` effect sizes. The overall effect of imitation measured using only tongue protrusion compared to mouth opening was large and significant (b = `r round(imput$b[2], 2)`, se = `r round(imput$se[2], 2)`, 95% CI = `r round(imput$ci.lb[2], 2)` to `r round(imput$ci.ub[2], 2)`, p = `r round(imput$pval[2], 3)`). 
## Sensitivity to individual studies

###  Leave-one-out analysis
```{r supplementary (leave1out), echo=FALSE, include=FALSE, warning=FALSE}
# not yet implemented for multilevel meta-analysis so only appropriate for meta-analysis with a single estimate per study
q <- leave1out(rmz)
rml <- rma.mv(gi.1, v, random = list(~ 1 | ID.L1, ~ 1 | ID.L2), data=dat)
```
The meta-analysis estimate excluding any single study did not significantly differ from the overall estimate (max estimate = `r round(max(q$estimate), 3)`, se = `r  round(q$se[q$estimate==max(q$estimate)], 2)`, deviance = `r round(max(q$estimate)-(rml$b),2)`, p = `r round(pt(((max(q$estimate))-(rml$b))/((q$se[q$estimate==max(q$estimate)])+(rml$se)),(length(q)-1)),3)`.

### Excluding Oostenbroek et al. (2016)
```{r supplementary (excluding Oostenbroek2016), echo=FALSE, include=FALSE, warning=FALSE}
tgt <- dat[dat$ID.L1 != "Oostenbroek2016",] # choose dataset
# meta-analysis
rmno <- rma.mv(gi.1,v,
              random = list(~ 1 | ID.L1, ~ 1 | ID.L2), 
              data=tgt)
# publication bias
tausq1 <- rmno$sigma2[1]
tausq2 <- rmno$sigma2[2]
egger1 <- lm(tgt$yi.1 ~ tgt$v, weights=1/(tgt$v+tausq1+tausq2))
segger1 <- summary(egger1)
egger2 = rma.mv(gi.1,v, mod = v, random = ~1|PaperID, data = tgt)
segger2 <- summary(egger2)
```
The sensitivity analysis included a total of `r rmno$k` effect sizes. The overall effect of imitation excluding all effects reported in Oostenbroek et al. (2016) was larger than the overall effect including it, and was still large and significant (b = `r round(rmno$b, 2)`, se = `r round(rmno$se, 2)`, 95% CI = `r round(rmno$ci.lb, 2)` to `r round(rmno$ci.ub, 2)`, p = `r round(rmno$pval, 3)`). The publication bias result was similar to the overall meta-analysis (t = `r round(segger1$coefficients[6],3)`, p = `r round(segger1$coefficients[8], 4)`).

### Excluding Meltzoff & Moore (1977)
```{r supplementary (excluding Meltzoff1977), echo=FALSE, include=FALSE, warning=FALSE}
tgt <- dat[dat$ID.L1 != "Meltzoff1977",] # choose dataset
# meta-analysis
rmno1 <- rma.mv(gi.1,v,
              random = list(~ 1 | ID.L1, ~ 1 | ID.L2), 
              data=tgt)
# publication bias
tausq1 <- rmno1$sigma2[1]
tausq2 <- rmno1$sigma2[2]
egger1 <- lm(tgt$yi.1 ~ tgt$v, weights=1/(tgt$v+tausq1+tausq2))
segger1 <- summary(egger1)
egger2 = rma.mv(gi.1,v, mod = v, random = ~1|PaperID, data = tgt)
segger2 <- summary(egger2)
```
The sensitivity analysis included a total of `r rmno1$k` effect sizes. The overall effect of imitation excluding all effects reported in Meltzoff & Moore (1977) was smaller than the overall effect including it, but was still large and significant (b = `r round(rmno1$b, 2)`, se = `r round(rmno1$se, 2)`, 95% CI = `r round(rmno1$ci.lb, 2)` to `r round(rmno1$ci.ub, 2)`, p = `r round(rmno1$pval, 3)`). The publication bias result was similar to the overall meta-analysis (t = `r round(segger1$coefficients[6],3)`, p = `r round(segger1$coefficients[8], 4)`).


## Alternative funnel plots
Publication bias test results given above. Funnel plots produced here.

### Tongue protrusion only

**Funnel plot 2: Tongue protrusion only.** Funnel plot with only tongue protrusion effects. Points are independent. Effect sizes from Meltzoff & Moore (1977) shown in red.

``` {r funnel plot 2, echo=FALSE, warning=FALSE}
tgt <- TP # choose dataset

# plot with ggplot
# modified from sakaluk.wordpress.com

# identify variables for the plot
estimate = rmTP$b
se = rmTP$se
tgt$se <- sqrt(tgt$v)
tgt$inv <- as.numeric(1/tgt$se)

# create lines for the funnel
se.seq=seq(0, max(tgt$se), 0.001)
ll95 = estimate-(1.96*se.seq)
ul95 = estimate+(1.96*se.seq)
ll99 = estimate-(3.29*se.seq)
ul99 = estimate+(3.29*se.seq)
meanll95 = estimate-(1.96*se)
meanul95 = estimate+(1.96*se)

# create data frame for plot lines
dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)

# identify the first published study with red coloured points
tgt$Meltzoff <- "0" 
tgt$Meltzoff[tgt$ID.L1=="Meltzoff1977"]="1"
tgt$Meltzoff <- as.numeric(tgt$Meltzoff)

# create data frame for plot points
yi <- tgt$yi.1
sd <- tgt$se
M <- tgt$Meltzoff
newdat <- cbind.data.frame(yi,sd,M)
newdat$M <- as.factor(newdat$M)

# make the plot
fp = ggplot(aes(x = sd, y = yi), data = newdat) +
  geom_point(aes(color=M,shape=19), data=newdat) +
  scale_color_manual(values=c("black", "red")) +
  scale_shape_identity() +
  xlab('Standard Error') + ylab('Effect size')+
  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
  geom_segment(aes(x = min(se.seq), y = estimate, xend = max(se.seq), yend = estimate), data=dfCI) +
  scale_x_reverse()+
  coord_flip()+
  theme_bw() +
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.border=element_blank(),
        axis.line=element_line(),
        legend.position='none') # APA format

fp

````

### Single estimate per independent sample
**Funnel plot 3: Single estimate per independent sample.** Funnel plot with single average estimate per independent sample. Points are independent. Effect sizes from Meltzoff & Moore (1977) shown in red.

``` {r funnel plot 3, echo=FALSE, warning=FALSE}

tgt <- z # choose dataset

# plot with ggplot
# modified from sakaluk.wordpress.com

# identify variables for the plot
estimate = rmz$b
se = rmz$se
tgt$inv <- as.numeric(1/tgt$seN)

# create lines for the funnel
se.seq=seq(0, max(tgt$seN), 0.001)
ll95 = estimate-(1.96*se.seq)
ul95 = estimate+(1.96*se.seq)
ll99 = estimate-(3.29*se.seq)
ul99 = estimate+(3.29*se.seq)
meanll95 = estimate-(1.96*se)
meanul95 = estimate+(1.96*se)

# create data frame for plot lines
dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)

# identify the first published study with red coloured points
tgt$Meltzoff <- "0" 
tgt$Meltzoff[tgt$Paper=="Meltzoff1977_1"]="1"
tgt$Meltzoff[tgt$Paper=="Meltzoff1977_2"]="1"
tgt$Meltzoff <- as.numeric(tgt$Meltzoff)

# create data frame for plot points
yi <- tgt$estimate
sd <- tgt$seN
M <- tgt$Meltzoff
newdat <- cbind.data.frame(yi,sd,M)
newdat$M <- as.factor(newdat$M)

# make the plot
fp = ggplot(aes(x = sd, y = yi), data = newdat) +
  geom_point(aes(color=M,shape=19), data=newdat) +
  scale_color_manual(values=c("black", "red")) +
  scale_shape_identity() +
  xlab('Standard Error') + ylab('Effect size')+
  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
  geom_segment(aes(x = min(se.seq), y = estimate, xend = max(se.seq), yend = estimate), data=dfCI) +
  scale_x_reverse()+
  coord_flip()+
  theme_bw() +
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.border=element_blank(),
        axis.line=element_line(),
        legend.position='none') # APA format

fp

````

### Results from different ways of calculating publication bias with multilevel data 
```{r supplementary (calculating bias), echo=FALSE, include=FALSE, warning=FALSE}
tgt <- dat # choose dataset
### multilevel random-effects model
rml <- rma.mv(gi.1, v, random = list(~ 1 | ID.L1, ~ 1 | ID.L2), data=tgt)

# adapted Egger test from Moreno et al 2009
egger0 <- lm(tgt$yi.1 ~ tgt$v, weights=1/(tgt$v))
segger0 <- summary(egger0)
# adding levels extending the random effect model by adding the extra variance term to the weight (method 1)
tausq1 <- rml$sigma2[1]
tausq2 <- rml$sigma2[2]
egger1 <- lm(tgt$yi.1 ~ tgt$v, weights=1/(tgt$v+tausq1+tausq2))
segger1 <- summary(egger1)

# adding a random effects term to meta-analysis model with variance as a predictor (method 2)
egger2 = rma.mv(gi.1,v, mod = v, random = ~1|PaperID, data = tgt)
segger2 <- summary(egger2)

# two-step method fixed and random effects
egger3 = regtest(rmz, model="lm", predictor="sei", method="FE") # fixed effects
egger4 = regtest(rmz, model="lm", predictor="sei", method="RE") # random effects

coef<-NULL
coef$method <- c("Multilevel random effects  model",
                 "Multilevel extended model",
                 "Multilevel model using rma.mv",
                 "Two-step method fixed effects model",
                 "Two-step method random effects model")
coef$t <- c(segger0$coefficients[6],
            segger1$coefficients[6],
            segger2$zval[2],
            egger3$zval,
            egger4$zval)
coef$p <- c(segger0$coefficients[8],
            segger1$coefficients[8],
            segger2$pval[2],
            egger3$pval,
            egger4$pval)
```
**Table S1.** Results for different ways of calculating publication bias.

```{r supplementary(kable), echo=FALSE, warning=FALSE}
coef<-as.data.frame(coef)
kable(coef, digits=3)
```